
\documentclass{book}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amssymb}
\usepackage{eurosym}
\usepackage{amsfonts}
\usepackage{amsmath}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2606}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Monday, July 27, 2009 13:07:40}
%TCIDATA{LastRevised=Sunday, February 28, 2010 15:36:40}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Standard LaTeX\Standard LaTeX Book">}
%TCIDATA{CSTFile=40 LaTeX Book.cst}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\input{tcilatex}

\begin{document}

\frontmatter
\title{GEOCAM\\
Geometric Evolutions on Computational Abstract Manifolds}
\author{Daniel Champion, David Glickenstein, Yuliya Gorlina, \and Alex
Henniges, Kurtis Norwood, Jeff Taft, \and Joseph Thomas, Andrea Young}
\date{Summer 2009}
\maketitle
\tableofcontents

\chapter*{Preface}

\markboth{PREFACE}{PREFACE}This is is the preface. It is an unnumbered
chapter. The \verb|markboth| TeX field at the beginning of this paragraph
sets the correct page heading for the Preface portion of the document. The
preface does not appear in the table of contents.

\mainmatter

\part{Introductory Information}

%TCIMACRO{\QSubDoc{Include introduction}{\input{introduction.tex}}}%
%BeginExpansion
\input{introduction.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include cplusplus}{\input{cplusplus.tex}}}%
%BeginExpansion
\input{cplusplus.tex}%
%EndExpansion

\part{System Documentation}

%TCIMACRO{\QSubDoc{Include system}{\input{system.tex}}}%
%BeginExpansion
\input{system.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include subsystems}{\input{subsystems.tex}}}%
%BeginExpansion
\input{subsystems.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include functions}{\input{functions.tex}}}%
%BeginExpansion
\input{functions.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include classes}{\input{classes.tex}}}%
%BeginExpansion
\input{classes.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include Geoquants}{\input{Geoquants.tex}}}%
%BeginExpansion
\input{Geoquants.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include Combinatorics}{\input{Combinatorics.tex}}}%
%BeginExpansion
\input{Combinatorics.tex}%
%EndExpansion

%TCIMACRO{\QSubDoc{Include Miscellaneous}{\input{Miscellaneous.tex}}}%
%BeginExpansion
\input{Miscellaneous.tex}%
%EndExpansion

\part{Theory}

%TCIMACRO{\QSubDoc{Include glossary}{\input{glossary.tex}}}%
%BeginExpansion
\input{glossary.tex}%
%EndExpansion

\bigskip

\appendix

\chapter{Appendix}

The appendix fragment is used only once. Subsequent appendices can be
created using the Chapter Section/Body Tag.

\backmatter

\chapter{Afterword}

The back matter often includes one or more of an index, an afterword,
acknowledgements, a bibliography, a colophon, or any other similar item. In
the back matter, chapters do not produce a chapter number, but they are
entered in the table of contents. If you are not using anything in the back
matter, you can delete the back matter TeX field and everything that follows
it.

\end{document}
