%TCIDATA{Version=5.00.0.2606}
%TCIDATA{LaTeXparent=0,0,functions.tex}
                      

%%%%% BEGINNING OF DOCUMENT BODY %%%%%
% html: Beginning of file: `clean.html'
% DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01//EN"
%  This is a (PRE) block.  Make sure it's left aligned or your toc title will be off. 

\section*{\texttt{Geoquant::At}}

\label{f0}

\begin{quotation}
{\small }
\end{quotation}

\begin{verbatim}
{\small Geoquant*  Geoquant::At(Simplex  s1,  ...)
}
{\small   
}
\end{verbatim}

\subsection*{Key Words}

\begin{quotation}
geoquant, recalculate, dependent, triposition, simplex
\end{quotation}

\subsection*{Authors}

\begin{itemize}
\item Joseph Thomas
\end{itemize}

\subsection*{Introduction}

\begin{quotation}
The \texttt{At} function is defined for every type of geoquant as a way to
retrieve that quantity. Once the quantity is retrieved, a value can be set
or asked of the quantity. A quantity is retrieved by providing a list of
simplices that describe the position of the quantity in the triangulation.
\end{quotation}

\subsection*{Subsidiaries}

\begin{quotation}
Functions:
\end{quotation}

\begin{itemize}
\item getSerialNumber
\end{itemize}

\begin{quotation}
Global Variables: mapLocal Variables: possible list of simplices
\end{quotation}

\subsection*{Description}

\begin{quotation}
The \texttt{At} function is a little di\"{\i}\&not;erent for every type of
geoquant, but in all cases it is a static function for that class that
serves as an object retrieval in place of a constructor. The function takes
as a parameter a list of simplices which may be di\"{\i}\&not;erent for each
type of geoquant. The list is the natural description of where the quantity
is in the triangulation. For example, a radius is described by a vertex,
whereas an angle is described as a vertex on a certain face. The At function
returns a pointer to the requested quantity.

When the \texttt{At} function is called, it searches a local map for a
quantity with the given list of simplices. If it is found, a pointer to that
quantity in the map is simply returned. If it is not found, the quantity is
constructed and placed into the map. If the construction of the object
requires other types of quantities not yet created, then these will be
constructed automatically at this time. Lastly, this quantity is returned.

The constructor is hidden from the user for several reasons. The \"{\i}%
\&not;rst is that this avoids redundant construction and the need for an
encapsulating object to hold a large set of geoquants (like the Geometry
class in a previous version). In the same vein, the need for an initial
build step and a required order of construction is removed. In addition,
this is an e\"{\i}\&not;ciency improvement as quantities that are never
requested are never created, decreasing memory use and large dependency
trees which can take a while for an \texttt{invalidate} to traverse.
\end{quotation}

\subsection*{Practicum}

\begin{quotation}
Example:{\small }
\end{quotation}

\begin{verbatim}
{\small 
//  Get  the  Radius  quantity  from  the  first  vertex  in  the  triangulation.
}
{\small Radius  *r  =  Radius::At(Triangulation::vertexTable[0]);
}
{\small //  Get  the  angle  of  vertex  v  incident  on  face  f
}
{\small Vertex  v;
}
{\small Face  f;
}
{\small ...
}
{\small EuclideanAngle  *ang  =  EuclideanAngle::At(v,  f);
}
{\small   
}
\end{verbatim}

\subsection*{Limitations}

\begin{quotation}
The \texttt{At} function is limited in that a speci\"{\i}\&not;c set of
simplices will always return the exact same object. While this is in fact
the design goal, this can limit one\^as ability to modify an object as a
change in one place will a\"{\i}\&not;ect its use elsewhere in the code. The
function also will require the user to handle pointers, a powerful yet
fragile and sometimes daunting aspect of the programming language.
\end{quotation}

\subsection*{Revisions}

\begin{itemize}
\item subversion 761, 6/12/09: A working copy of \texttt{At} and the
Geoquant system.
\end{itemize}

\subsection*{Testing}

\begin{quotation}
The \texttt{At} function was tested in small modularized systems, then
tested in a three dimensional \"{\i}\&not;ow, which required many varied
uses of \texttt{At}. Some retrieved quantities had their values set while
others had their values accessed and compared with what mathematica
calculations predicted.
\end{quotation}

\subsection*{Future Work}

\begin{quotation}
No future work is planned at this time.
\end{quotation}

% html: End of file: `clean.html'

%%%%% END OF DOCUMENT BODY %%%%%
% In the future, we might want to put some additional data here, such
% as when the documentation was converted from wiki to TeX.
%
