%TCIDATA{Version=5.00.0.2606}
%TCIDATA{LaTeXparent=0,0,geocam.tex}
                      
%TCIDATA{ChildDefaults=chapter:1,page:1}


\chapter{Glossary}

\begin{description}
\item[center (of a simplex)] 

\item[circle power] Given a circle $C$ and a point $P$, let $L$ be the line
through the point $P$ that passes through the center of the circle. \ Let $A$
and $B$ be the intersection points of $L$ with the circle.\ Define a signed
distance $\left\Vert \overline{PX}\right\Vert $ for a line segment $%
\overline{PX}$ to be negative if the line segment lies entirely within the
circle, and positive otherwise. \ The \textit{circle power} of $P$ relative
to $C$, denoted by $pow_{C}\left( P\right) $, is given by:%
\[
pow_{C}\left( P\right) =\left\Vert \overline{PA}\right\Vert \left\Vert 
\overline{PB}\right\Vert .
\]%
Alternatively, if $C$ is defined implicitly by $\left( x-x_{c}\right)
^{2}+\left( y-y_{c}\right) ^{2}=r_{c}^{2}$, then the circle power can be
expressed as:%
\[
pow_{C}\left( P\right) =\left( x-x_{c}\right) ^{2}+\left( y-y_{c}\right)
^{2}-r_{c}^{2}.
\]

\item[common power point] The point of the plane (or $%
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
^{3}$) containing a decorated triangle (or tetrahedron) that has the same
circle power with respect to each of the weight circles. \ 

\item[decorated simplex (edge, triangle, tetrahedron,...)] A simplex is
called \textit{decorated} when weights are assigned to the vertices of the
simplex and then actualized by embedding the simplex into Euclidean space
together with spheres centered at the vertices with radii determined by the
weights. \ The orthocircle (if one exists) is sometimes considered part of
the decorated simplex when appropriate.

\item[edge curvature] Given a three-dimensional piecewise flat manifold $%
\left( M,\mathcal{T},d\right) $, the \textit{edge curvature} along an edge $%
\left\{ i,j\right\} $, measures how much that edge differs from Euclidean
space. \ Specifically, the edge curvature $K_{ij}$ is given by 
\[
K_{ij}=\left( 2\pi -\sum\limits_{\substack{ k,l\text{, such that} \\ \left\{
i,j,k,l\right\} \in \mathcal{T}}}\beta _{ij,kl}\right) l_{ij},
\]%
where $l_{ij}$ is the edge length, and $\beta _{ij,kl}$ is the dihedral
angle of the edge $\left\{ i,j\right\} $ of the tetrahedron $\left\{
i,j,k,l\right\} $. \ In a triangulation of three-dimensional Euclidean space 
$K_{ij}=0$ for all edges. \ 

\item[Einstein constant] For a 3-dimensional piecewise flat manifold $\left(
M,\mathcal{T},d\right) $, the \textit{Einstein constant} $\lambda $ is given
by%
\[
\lambda =\frac{\mathcal{EHR}\left( M,\mathcal{T},d\right) }{3\mathcal{V}},
\]%
where $\mathcal{EHR}\left( M,\mathcal{T},d\right) $ is the
Einstein-Hilbert-Regge functional and $\mathcal{V}$ is the total volume.

\item[Einstein metric] Given a 3-dimensional piecewise flat manifold $\left(
M,\mathcal{T},d\right) $, we say that $d$ is an \textit{Einstein metric}
provided there exists $\lambda \in \mathbb{R}$ such that for all edges $%
\left\{ i,j\right\} $ in the triangulation we have:%
\[
K_{ij}=\lambda l_{ij}\frac{\partial \mathcal{V}}{\partial l_{ij}},
\]%
where $K_{ij}$ is the edge curvature, $l_{ij}$ is the edge length, and $%
\mathcal{V}$ is the total volume. By summing both sides, we see that $%
\lambda $ is the Einstein constant.

\item[hinge] A hinge consists of a pair of triangles that share a single
edge. \ Often, two adjacent triangles in a simplicial surface are identified
as a hinge while studying the edge they share. \ Any hinge can be
isometrically embedding $%
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
^{2}$. \ There is a natural generalization to three (and higher) dimensions
for two tetrahedra sharing a face. \ Similarly, this generalized hinge can
be isometrically embedded in $%
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
^{3}$. \ 

\item[inversive distance] Start with a decorated edge $e_{ij}$, that is, an
edge of length $l_{ij}$ with weight circles of radius $r_{i},r_{j}$ centered
on its vertices. \ The inversive distance $\eta _{ij}$ of the edge $e_{ij}$
can be calculated with the formula:%
\[
\eta _{ij}=\frac{l_{ij}^{2}-r_{i}^{2}-r_{j}^{2}}{2r_{i}r_{j}}.
\]%
When the two weight circles intersect with angle $\theta _{ij}$, we have the
simple formula:%
\[
\eta _{ij}=-\cos \left( \theta _{ij}\right) .
\]%
The former formula was obtained by using the law of cosines and solving for
the $\cos \left( \theta _{ij}\right) $ term. \ When the weight circles do
not intersect and do not contain one or the other $\eta _{ij}>1$. \ When the
weight circles intersect at some angle then $-1\leq \eta _{ij}\leq 1$. \ If
one weight circle contains the other we have $\eta _{ij}<1$. \ 

\item[manifold] A second countable, Hausdorff topological space $M$ is a 
\textit{manifold} provided there is an integer $n>0$ such that for each $%
x\in M$ there is an open set $U_{x}$ containing $x$ and a homeomorphism $%
h_{x}:U_{x}\rightarrow B\left( 1,0\right) \subset 
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
^{n}$. \ A discrete (or piecewise flat) space is a manifold provided the
sub-simplices satisfy the following conditions:

\item Dimension 2:

\begin{itemize}
\item All edges have exactly two adjacent faces.

\item For a vertex $v$, the faces incident upon $v$ can be arranged
cyclically as $f_{1},f_{2},...,f_{N},f_{1},...$ so that there is an edge
(containing $v$ as an endpoint) between each pair of consecutive faces $%
f_{i},f_{i+1}$, where $N+1$ is understood to be $1$. \ 
\end{itemize}

\item Dimension 3:

\begin{itemize}
\item All faces have exactly two adjacent tetrahedra.

\item For each edge $e$, the tetrahedra incident upon $e$ can be arranged
cyclically as $\sigma _{1},\sigma _{2},...,\sigma _{M},\sigma _{1},...$ so
that there is a face (containing $e$ as an edge) between each pair of
consecutive tetrahedra $\sigma _{i},\sigma _{i+1}$ where $M+1$ is understood
to be $1$. \ 

\item For each vertex $v$, the number of incident edges, faces and
tetrahedra, $E,F,T$, respectively (including multiple occurrences) satisfy:%
\[
E-F+T=2.
\]
\end{itemize}

\item More generally, given a simplicial manifold $M$ of dimension $n$, and
a sub-simplex $\sigma $ of dimension $m<n$, the sub-simplices of $M$ of
dimension greater than $m$ have the structure of $S^{n-m-1}$.

\item[orthocircle] Given a decorated triangle, provided the common power
point is outside all of the weight circles, there exists a circle that is
orthogonal to each of the weight circles. \ That is, the \textit{orthocircle}
is the circle that intersects each of the weight circles orthogonally. \ The
orthocircle does not exist when the common power point is on or inside all
three circles, however if the common power point is at infinity, there is a
line that is orthogonal to the three weight circles which will also be
identified as the orthocircle.

\item[piecewise flat manifold] A triple $\left( M,\mathcal{T},\ell \right) $
where $\left( M,\mathcal{T}\right) $ is a triangulated manifold with
triangulation $\mathcal{T}$ and $\ell :E\rightarrow \mathbb{R}_{+}$ is a
function of the edges such that endowing the edges with lengths $\ell $
gives each simplex the structure of a Euclidean simplex. We sometimes call
two piecewise flat manifolds $\left( M,\mathcal{T},\ell \right) $ and $%
\left( M,\mathcal{T}^{\prime },\ell ^{\prime }\right) $ isometric if they
induce the same metric space structure, or if one can be reached from the
other by a sequence of metric Pachner moves (flips).\ 

\item[piecewise flat, metrized manifold] A triple $\left( M,\mathcal{T}%
,d\right) $ where $\left( M,\mathcal{T}\right) $ is a triangulated manifold
and $d:E^{+}\rightarrow \mathbb{R}$ is a function of oriented edges such
that if one defines $\ell _{ij}=d_{ij}+d_{ji}$ then $\left( M,\mathcal{T}%
,\ell \right) $ is a piecewise flat manifold and such that each simplex has
a uniquely determined center.

\item[triangulation] A collection of $n$-dimensional simplices $\mathcal{T}$
together with pairwise identifications for the $\left( n-1\right) $%
-dimensional faces of the simplices. \ More restrictions are needed to
ensure that the resultant space is a manifold. \ Alternatively, given a
space $M$ of dimension $n$, a \textit{triangulation} of $M$ is a subdivision
of $M$ into components $\left\{ \sigma _{i}\right\} $ by (hyper)surfaces (of
dimension $n-1$) so that each component is homeomorphic to an $n$%
-dimensional ball, and each component is combinatorially (as determined by
the subdivisions) equivalent to an $n$-simplex. \ 

\item[pseudo manifold] A discrete \textit{pseudo manifold} is a relaxation
of the manifold conditions for a discrete space. \ For dimensions two and
three, the bullet conditions given in the entry on manifold may no longer
hold. \ However, the manifold condition is still (trivially) satisfied in
the interior of all top dimensional simplices.

\item[weighted triangulation (or hinge)] A triangulation together with a map 
$w:V\rightarrow 
%TCIMACRO{\U{211d} }%
%BeginExpansion
\mathbb{R}
%EndExpansion
$, where $V$ is the set of vertices of the triangulation. \ Each simplex
becomes a decorated simplex. \ 

\item[dimension] A manifold has the property that every point has a
neighborhood homeomorphic to an open subset of $\mathbb{R}^{n}.$ By the
Invariance of Dimension theorem, $n$ must be locally constant (i.e., every
point in a given connected component must have the same dimension. We say $n$
is the dimension of the manifold. For a triangulated manifold, the dimension
of the manifold is the dimension of the highest-dimensional simplices in the
triangulation.

\item[metric] Metric can have a number of meanings: (1) a metric can mean a
distance function for a metric space, (2)\ a Riemannian metric is an inner
product at each tangent space which varies smoothly with the basepoint. It
can also be described as a symmetric, positive definite 2-tensor field, (3)
a Lorenzian metric is a symmetric bilinear form at each tangent space with
signature +,-,-,...,- or -,+,...+ which varies smoothly with the basepoint.

\item[curvature] 

\item[scalar curvature] For a Riemannian manifold $\left( M,g\right) $,
scalar curvature is a function $R:M\rightarrow \mathbb{R}$ gotten from the
full trace of the Riemannian curvature tensor. For a piecewise flat,
metrized 3-manifold, the scalar curvature measure $K_{i}$ is defined as 
\[
K_{i}=\sum_{j}\frac{K_{ij}}{\ell _{ij}}d_{ij}.
\]

\item[constant scalar curvature] For a Riemannian manifold $\left(
M,g\right) $, this means that the scalar curvature function $R:M\rightarrow 
\mathbb{R}$ is a constant function. For a piecewise flat, metrized
3-manifold, this means that the scalar curvature measure is a constant
multiple of the volume measure, i.e., 
\[
K_{i}=\lambda V_{i},
\]%
for all vertices $i,$ where $K_{i}=\sum_{j}\frac{K_{ij}}{\ell _{ij}}d_{ij}$
and $V_{i}=\ell _{ij}\frac{\partial \mathcal{V}}{\partial \ell _{ij}}=\frac{1%
}{3}\sum_{j,k,\ell }h_{ijk,\ell }A_{ijk},$ where $\mathcal{V}$ is the total
volume, $h_{ijk,\ell }$ is the (signed) height of the center to face $%
\left\{ i,j,k\right\} $ and $A_{ijk}$ is the area of face $\left\{
i,j,k\right\} .$

\item[geometric flow] A geometric flow is a differential equation on a
geometry (loosely defined) which depends only on geometric quantities
(usually curvatures). Usual examples are Ricci flow, mean curvature flow,
and Yamabe flow on Riemannian manifolds. On discrete geometries, there are
discrete Ricci and Yamabe flows.

\item[curvature flow] 

\item[Yamabe flow] 

\item[normalized total scalar curvature functional] 

\item[Einstein-Hilbert functional] Given a Riemannian manifold $\left(
M,g\right) ,$ the Einstein-Hilbert functional $\mathcal{EH}\left( M,g\right) 
$ is defined by 
\[
\mathcal{EH}\left( M,g\right) =\int_{M}RdV
\]%
where $R$ is the scalar curvature of $g$ and $dV$ is the volume form of $g.$
The functional is constant on two-dimensional manifolds, giving $4\pi $
times the Euler characteristic. In higher dimensions, its critical points
are Ricci flat (i.e., the Ricci tensor is zero) and critical points
restricted to metrics of a fixed volume are Einstein manifolds.

\item[Einstein-Hilbert-Regge functional] Given a piecewise flat manifold $%
\left( M^{n},\ell \right) $, the Einstein-Hilbert-Regge functional $\mathcal{%
EHR}\left( M,\ell \right) $ is defined by 
\[
\mathcal{EHR}\left( M,\ell \right) =\sum_{\sigma ^{n-2}}K\left( \sigma
^{n-2}\right) ,
\]%
where $K\left( \sigma ^{n-2}\right) $ is $2\pi $ minus the sum of the angles
at $\sigma ^{n-2}$ times the volume $V\left( \sigma ^{n-2}\right) $ of the
simplex $\sigma ^{n-2}.$ In particular, for $n=3,$ we have 
\[
\mathcal{EHR}\left( M^{3},\ell \right) =\sum_{\left\{ i,j\right\}
}K_{ij}=\sum_{\left\{ i,j\right\} }\left( 2\pi -\sum_{k,\ell }\beta
_{ij,k\ell }\right) \ell _{ij},
\]%
where $\beta _{ij,k\ell }$ is the dihedral angle at edge $\left\{
i,j\right\} $ in $\left\{ i,j,k,\ell \right\} .$

\item[conformal class] On a smooth Riemannian manifold $\left( M,g\right) ,$
the conformal class $\left[ g\right] $ is the equivalence class of all
Riemannian manifolds $\left( M,e^{f}g\right) ,$ where $f$ is a smooth
function. On a metrized piecewise flat manifold $\left( M,T,d\right) $, the
conformal class $\left[ d\right] $ is the equivalence class .....

\item[conformal deformation] 

\item[min-max procedure] 

\item[Yamabe constant] On a closed manifold $M,$ the Yamabe constant (also
called the $\sigma $-constant) is the number 
\[
\sigma \left( M^{n}\right) =\sup_{g}\inf_{g^{\prime }\in \left[ g\right] }%
\frac{\mathcal{EH}\left( M,g^{\prime }\right) }{V\left( M,g^{\prime }\right)
^{2/n}},
\]%
where the $\sup $ is over all metrics and the $\inf $ is over all metrics in
the same conformal class $\left[ g\right] $ as $g.$

\item[flip] 

\item[Pachner move] 

\item[flip algorithm] 

\item[convex hinge] 

\item[nonconvex hinge] 

\item[bone] 

\item[Delaunay triangulation (or hinge)] 

\item[weighted Delaunay triangulation] 

\item[Voronoi diagram (or cell)] 

\item[weighted Voronoi diagram (or cell)] 

\item[power diagram (or cell)] 

\item[negative triangles] 

\item[dual, Poincare dual] 

\item[dual length] 

\item[dual volume] 
\end{description}
