%TCIDATA{Version=5.00.0.2606}
%TCIDATA{LaTeXparent=0,0,functions.tex}
                      

%%%%% BEGINNING OF DOCUMENT BODY %%%%%
% html: Beginning of file: `clean.html'
% DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01//EN"
%  This is a (PRE) block.  Make sure it's left aligned or your toc title will be off. 

\section*{\texttt{pause}}

\label{f0}

\begin{quotation}
{\small }
\end{quotation}

\begin{verbatim}
{\small    void pause();
}
{\small    void pause(char *fmt, ...);
}
{\small    
}
\end{verbatim}

\subsection*{Key Words}

\begin{quotation}
pause, print
\end{quotation}

\subsection*{Authors}

\begin{quotation}
Alex Henniges
\end{quotation}

\subsection*{Introduction}

\begin{quotation}
The \texttt{pause} freezes the current process until the user presses the 
\textbf{enter} key. This function also allows the user to print information
at the pause line.
\end{quotation}

\subsection*{Subsidiaries}

\begin{quotation}
Functions:
\end{quotation}

\begin{itemize}
\item \texttt{vprintf}

\item \texttt{scanf}

\item \texttt{fflush}
\end{itemize}

\begin{quotation}
Global Variables:

Local Variables:
\end{quotation}

\subsection*{Description}

\begin{quotation}
The \texttt{pause} function is designed to place break points in the code
that will stop the process until the user presses the enter key. There are
several uses to this. A standard one is debugging as it can allow a
programmer to step through a procedure. While there are usually similar
debugging options in code editors, this function can be added and removed
easily from within the code. The second use is that the console for programs
will close immediately after execution with some editors. Without a way to
freeze the program, the console would close before the data could be read
and interpreted.

There are two options for this \texttt{pause} function. If the default pause
is used, the following message will be printed:``PAUSE...''Pressing the 
\textbf{enter} key will resume the process. The function can also print out
a message provided to it. This uses the \texttt{vprintf} function so that
the printed information can be formatted text. The user must still press 
\textbf{enter} to resume when this form is used. Pressing other keys will
not affect the program.

Historically, the project has used {\small }
\end{quotation}

\begin{verbatim}
{\small   system("PAUSE");
}
{\small   
}
\end{verbatim}

\begin{quotation}
to pause the program. However, this can only be used on a Windows machine, a
limiting factor that we wish to remove from the project.
\end{quotation}

\subsection*{Practicum}

\begin{quotation}
Example:{\small }
\end{quotation}

\begin{verbatim}
{\small   pause("Done...press enter to exit."); // PAUSE
}
{\small   
}
\end{verbatim}

\subsection*{Limitations}

\begin{quotation}
One limitation of the \texttt{pause} function is that it only resumes after
pressing the \textbf{enter} key. This is compared to the former pause
function (see above) that would resume after pressing any key. This could
also be considered an improvement.
\end{quotation}

\subsection*{Revisions}

\begin{itemize}
\item subversion 909, 8/4/09: Added the fully functional \texttt{pause}
function.
\end{itemize}

\subsection*{Testing}

\begin{quotation}
The \texttt{pause} function has been tested simply through using it
extensively.
\end{quotation}

\subsection*{Future Work}

\begin{quotation}
No future work is planned at this time.
\end{quotation}

% html: End of file: `clean.html'

%%%%% END OF DOCUMENT BODY %%%%%
% In the future, we might want to put some additional data here, such
% as when the documentation was converted from wiki to TeX.
%
