%TCIDATA{Version=5.00.0.2606}
%TCIDATA{LaTeXparent=0,0,functions.tex}
                      

%%%%% BEGINNING OF DOCUMENT BODY %%%%%
% html: Beginning of file: `clean.html'
% DOCTYPE HTML PUBLIC "-//W3C//DTD HTML 4.01//EN"
%  This is a (PRE) block.  Make sure it's left aligned or your toc title will be off. 

\section*{\texttt{printResultsNum}}

\label{f0}{\small }
\begin{verbatim}
{\small 
        void printResultsNum(char* fileName, vector<double>* radii, vector<double>* curvs)
}
\end{verbatim}

\subsection*{Key Words}

radii, curvatures, file, flow, vertex, print

\subsection*{Authors}

Alex Henniges

\subsection*{Introduction}

The \texttt{printResultsNum} function prints out the results of a curvature
flow, with the results grouped by each vertex of the triangulation but
without labels. This format is used for when a program, (GUI, Matlab, etc)
needs to parse the data. These results will be written to the file given by 
\texttt{filename}.

\subsection*{Subsidiaries}

Functions:

Global Variables:

Local Variables: \texttt{int vertSize}, \texttt{int numSteps}

\subsection*{Description}

Prints the results of a curvature flow into the file given by \texttt{%
filename}. The results, that is, the radii and curvature values, are given
by vectors of doubles. Most commonly, these vectors are taken from the
Approximator class after the flow is run. The \texttt{printResultsNum}
function determines the number of vertices of the current triangulation and
the total number of steps are then derived from this and the size of the
vectors.

There are several ways to display the results. The \texttt{printResultsNum}
function groups by vertex but provides no labels. This means that for each
vertex of the triangulation, the radii (first column) and curvature (second
column) values for each step is given. This format is used for when a
program, (GUI, Matlab, etc) needs to parse the data. Therefore, it would be
difficult for a human to read, but allows the computer to do so much easier.
An example is shown below. Other formats are given by printResultsStep,
printResultsVertex, print3DResultsStep.

\subsection*{Practicum}

Example: {\small }
\begin{verbatim}
{\small     // Print the results of a curvature flow with
}
{\small     // Approximator app into file "ODEResult.txt"
}
{\small 
    printResultsNum("./ODEResults.txt", app->radiiHistory, app->curvHistory); 
}
\end{verbatim}

The output of such an example may then be {\small }
\begin{verbatim}
{\small          :
}
{\small          :
}
{\small       0.8272160717        3.1425515910
}
{\small       0.8272081392        3.1425294463
}
{\small       0.8272003900        3.1425078130
}
 
{\small       1.0000000000        3.1415926536
}
{\small       1.0000000000        3.5987926375
}
{\small       0.9954280002        3.5877016632
}
{\small       0.9909873062        3.5768691746
}
{\small       0.9866737711        3.5662905388
}
{\small          :
}
{\small          :
}
\end{verbatim}

\subsection*{Limitations}

Currently the \texttt{printResultsNum} function is limited in the
information it prints. As our curvature flow has evolved to record
additional information such as volumes, it may be time to explore a more
robust form for displaying results. As there is considerable dependence on
the Approximator for the data vectors, it may be wise to place this and
similar functions in the \mbox{$[$}CurvatureFlow Approximator\mbox{$]$}
class.

\subsection*{Revisions}

\textbf{\ subversion 545, 9/29/08: Moved the printing of results out of
calcFlow and into a new function. }  subversion 783, 6/18/09: Small
modifications in response to changes in the Approximator class.

\subsection*{Testing}

The \texttt{printResultsNum} function was tested by running multiple
curvature flows and printing the results. It was considered working when the
format of the data was as desired.

\subsection*{Future Work}

\textbf{\ 6/29 - Recreate the print functions to print more data and be more
flexible.}  6/29 - Move the print functions into the Approximator class.

% html: End of file: `clean.html'

%%%%% END OF DOCUMENT BODY %%%%%
% In the future, we might want to put some additional data here, such
% as when the documentation was converted from wiki to TeX.
%
